\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}
\hypersetup{colorlinks=true, urlcolor=blue}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Hamza Bashir} \\ \vspace{3pt}
    \small +92 332 057 3993 $|$ hamzabashir1289@gmail.com $|$ 
    \href{https://linkedin.com/in/hamza-bashir-a56281247/}{LinkedIn} $|$ 
    \href{https://hamzabashir.vercel.app}{Portfolio} \\
    Islamabad, Pakistan
    \vspace{-8pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Versatile Software Engineer with a strong track record in Full-Stack Web Development, Machine Learning, and Mobile Application Development. Proven ability to architect and deploy robust web platforms, real-time AI systems, and cross-platform mobile apps. Adept at leveraging modern frameworks, optimizing backend architectures, and applying advanced algorithms to solve complex real-world problems. Passionate about building scalable, high-performance applications and intelligent software solutions.}
\vspace{-3pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C/C++, JavaScript (TypeScript), Java, SQL, PHP, Dart} \\
     \textbf{Machine Learning \& AI}{: OpenCV, MediaPipe, Scikit-Learn, NumPy, Computer Vision} \\
     \textbf{Frontend \& Backend}{: MERN Stack, React (TypeScript), Node.js, Express, PHP, Laravel, TailwindCSS} \\
     \textbf{Databases}{: MySQL, MongoDB, PostgreSQL} \\
     \textbf{Developer Tools}{: Git/GitHub, Linux, VS Code, Android Studio, Flutter}
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Capital University of Science \& Technology (CUST)}{Sep 2022 -- Jul 2026}
{Bachelor of Science in Software Engineering}{Islamabad, Pakistan}
\resumeItemListStart
\resumeItem{\textbf{CGPA:} 3.20/4.00}
\resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Database Systems, Artificial Intelligence, Android \& Web Development}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Veclar Technologies}{Jul 2025 -- Sep 2025}
{MERN Stack Developer}{Rawalpindi, Pakistan}
\resumeItemListStart
\resumeItem{Developed real-world applications using React (TypeScript), Node.js/Express, PHP, and MySQL.}
\resumeItem{Built responsive UI using TailwindCSS, Bootstrap, and ShadCN UI.}
\resumeItem{Collaborated in a team-based development environment following modern development practices.}
\resumeItemListEnd

\resumeSubheading
{Arch Technologies}{Aug 2025 -- Sep 2025}
{Machine Learning Intern}{Pakistan}
\resumeItemListStart
\resumeItem{Worked on applied Machine Learning tasks including model development, experimentation, and evaluation.}
\resumeItemListEnd

\resumeSubheading
{Elevvo Pathways}{Aug 2025}
{Machine Learning Intern}{Remote}
\resumeItemListStart
\resumeItem{Implemented foundational ML workflows and data preprocessing pipelines.}
\resumeItemListEnd

\resumeSubheading
{SA Constructions}{Mar 2025 -- May 2025}
{Website Developer}{Islamabad, Pakistan}
\resumeItemListStart
\resumeItem{Developed a responsive WordPress site with user-friendly navigation, contact forms, and SEO optimization.}
\resumeItemListEnd

\resumeSubheading
{The Sescon (Pvt) Ltd}{Aug 2024 -- Sep 2024}
{Website Developer}{Islamabad, Pakistan}
\resumeItemListStart
\resumeItem{Developed a modern WordPress site with custom themes, project galleries, and optimized performance.}
\resumeItemListEnd

\resumeSubheading
{Pakistan Red Crescent Society (PRCS)}{Jul 2024 -- Aug 2024}
{Volunteer Service}{Islamabad, Pakistan}
\resumeItemListStart
\resumeItem{Proposed and supported First Aid and Emergency Crisis Training programs for schools.}
\resumeItem{Organized awareness seminars on emergency response protocols.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-14pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Smart Agriculture (FYP)} $|$ Flutter, Dart, Machine Learning, Firebase}{2026}
\resumeItemListStart
\resumeItem{Developed an AI-powered smart agriculture solution assisting Pakistani farmers in maximizing crop yield.}
\resumeItem{Integrated machine learning models for early crop disease detection and soil analysis.}
\resumeItem{Built a cross-platform mobile application utilizing a full-stack architecture for real-time data syncing.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Qalb: Islamic Advisor} $|$ Flutter, PHP, Vue.js, MySQL}{2026}
\resumeItemListStart
\resumeItem{Engineered a comprehensive Islamic advising mobile application with a dedicated admin panel.}
\resumeItem{Implemented a full-stack ecosystem featuring a native Android app and robust PHP backend API.}
\resumeItem{Designed an intuitive Vue.js dashboard for seamless content management and analytics.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Arrows Puzzle} $|$ JavaScript, Capacitor, HTML5/CSS3}{2026}
\resumeItemListStart
\resumeItem{Developed a logic-based puzzle game using modern JavaScript and web technologies.}
\resumeItem{Wrapped the web-based game with Capacitor to compile and deploy as a native mobile application.}
\resumeItem{Successfully published the interactive gaming application on the Google Play Store.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-14pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart

\resumeSubheading
{Python for Everybody Specialization}{2024}
{University of Michigan | Coursera}{}

\resumeSubheading
{C/C++ Programming Specialization}{2022}
{University of California, Santa Cruz | Coursera}{}

\resumeSubheading
{Aspire Leaders Program}{Dec 2025}
{Aspire Institute}{}

\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR-----------
\section{Extracurricular / Achievements}
\resumeItemListStart
\resumeItem{Dean’s Roll of Honor – Fall 2023.}
\resumeItem{Published technical articles on AI and software security topics.}
\resumeItem{Represented university in intercollegiate badminton tournaments.}
\resumeItem{Independent videographer producing cinematic real estate and event films.}
\resumeItemListEnd

\end{document}